### 2022-03-21 src/text/3-applications-subsections/multi-instrument-analysis.tex
added disclaimer about the spectral measurement

The result of the joint fit is displayed in Fig.~\ref{multi_instrument_analysis}.
We remark that the objective of this exercise is to show the interoperability of data

>>>>

The result of the joint fit is displayed in Fig.~\ref{multi_instrument_analysis}.
We remark that the objective of this exercise is illsutrative, we display the
flexibility of \gammapy in simultaneously fitting multi-isntrument data even at
different levels of reduction, we do not aim to privide a new measurement of the
Crab Nebula spectrum.
